---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis build status](https://travis-ci.org/venelin/PMMUsingSPLITT.svg?branch=master)](https://travis-ci.org/venelin/PMMUsingSPLITT)
[![Coverage status](https://codecov.io/gh/venelin/PMMUsingSPLITT/branch/master/graph/badge.svg)](https://codecov.io/github/venelin/PMMUsingSPLITT?branch=master)

# PMMUsingSPLITT

The goal of PMMUsingSPLITT is to provide a minimal example of how to use the SPLITT
C++ library in an R-package. See [this guide](https://venelin.github.io/SPLITT/articles/SPLITTRcppModules.html) for a tutorial.

## Installation

You can install the released version of PMMUsingSPLITT from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("PMMUsingSPLITT")
```

## Examples

* Calculating the likelihood of the PMM for a given tree, data and model parameters.
```{r}
library(ape)
library(PMMUsingSPLITT)

set.seed(10)

N <- 1000
x0 <- 0.1
alpha <- 1
theta <- 10
sigma2 <- 0.25
sigmae2 <- 1

tree <- rtree(N)

g <- rTraitCont(tree, model = "OU", root.value = x0,
                alpha = alpha, sigma = sqrt(sigma2),
                ancestor = FALSE)

x <- g + rnorm(n = N, mean = 0, sd = sqrt(sigmae2))

cat("logLikelihood using R:", PMMLogLik(x, tree, x0, sigma2, sigmae2), "\n")
cat("logLikelihood using R:", PMMLogLikCpp(x, tree, x0, sigma2, sigmae2), "\n")
```

* Performing a benchmark to measure the likelihood calculation times using different parallelization strategies:

```{r}
# N specifies the size of the phylogenetic tree. 
# Ntests specifies the number of executions in one time measurement 
# (the more the better, but also slower).
MiniBenchmark(N = 100, Ntests = 100)
MiniBenchmark(N = 1000, Ntests = 10)
MiniBenchmark(N = 10000, Ntests = 10)
```